Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-08-08 paper.tex
Updates in results and simulations

\subsection{Analysis}
\label{sec:analysis}
Based on a few simulations of Equations~\ref{eq:seeks-cluster-reads-1}
and~\ref{eq:seeks-multiple-reads}, we conjectured that the comparison
between Cluster reads and Multiple reads essentially depends on the
three Cluster reads cases. When Cluster reads merge incomplete block
rows (case 1), they are always outperformed by Multiple reads
(\textbf{prop 1}).  When Cluster reads merge complete block rows (case
2), the comparison between Cluster reads and Multiple reads depends on
the values of $D$ and $n$ (\textbf{prop 2}). When Cluster reads merge complete
block slices (case 3), Cluster reads and Multiple reads are equivalent
(\textbf{prop 3}).

\textbf{prop 1} \todo{do it!}

 \textbf{prop 2} is proven by Figure~\ref{fig:model-comparison} that
 shows two situations where Cluster reads and Multiple reads are
 alternatively better than each other.

 \textbf{prop 3} is easy to infer from
 equations~\ref{eq:seeks-cluster-reads-1}
 and~\ref{eq:seeks-multiple-reads} when assuming that $Rb$ is an exact
 multiple of $m$. In this case, both equations boils down to
 $n+\frac{Rb}{m}$.

\begin{figure}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison.pdf}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison-moreblocks.pdf}
  \caption{Number of seeks for Cluster reads vs Multiple reads when
    Cluster reads merge complete block rows (case 2), for D=3458 and
    b=2. Left: n=125; Right: n=64,000.}
  % Gnuplot file: scripts/model/model.gnplt
  \label{fig:model-comparison}
\end{figure}

@@

\subsubsection{Merge time breakdown}
Figure~\ref{fig:breakdowns-ssd} shows how the total merge time breaks
down to read, write, seek and overhead time for our algorithms. Naive
blocks and naive slices are shown as references. The huge difference
between naive blocks and naive slices is coming from both the seek
time and the write time, which suggests that seeking degrades the
write rate importantly in addition to introducing extra delays.
Cluster reads reduce the seek time and thus the read time very
substantially. Multiple reads almost anihilate the seek time and bring
the read time to a value comparable to naive slices.  The same
behavior is observed on HDD and on SSD, although the effect of seeking
is slightly lower on SSD, as expected. Read times are consistently and substantially lower than write times\todo{explain why}. The overhead time is small for
both Cluster reads and Multiple reads, although it is not negligible
for Multiple reads on HDD \todo{Overhead was not well measured for
  mreads. Needs to be redone.}.
\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-ssd.pdf}
    \caption{Cluster reads}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
    \caption{Multiple reads}
  \end{subfigure}
  \caption{Breakdown of total merge times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd-split.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd-split.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrite/cwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-ssd.pdf}
    \caption{Cluster writes}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
    \caption{Multiple reads}
  \end{subfigure}
  \caption{Breakdown of total split times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd-split}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

>>>>

\subsection{Analysis}
\label{sec:analysis}

Figure~\ref{fig:model-comparison} plots
Equations~\ref{eq:seeks-cluster-reads-1}
and~\ref{eq:seeks-multiple-reads} for different values of $n$. When
Cluster reads are in Case 1 or 2, they may outperform Multiple reads
only for large values of $n$. When Cluster reads are in case 3, they
are equivalent to Multiple reads; indeed, assuming that $Rb$ is an
exact multiple of $m$, Equations~\ref{eq:seeks-cluster-reads-1}
and~\ref{eq:seeks-multiple-reads} both boil down to $n+\frac{Rb}{m}$.

\begin{figure}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison.pdf}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison-moreblocks.pdf}
  \caption{Number of seeks for Cluster reads vs Multiple reads, for
    D=3458 and b=2. Left: n=125; Right: n=64,000. Case 1 and Case 2
    denote Cluster read configurations.}
  % Gnuplot file: scripts/model/model.gnplt
  \label{fig:model-comparison}
\end{figure}

@@

\subsubsection{Merge time breakdown}
Figure~\ref{fig:breakdowns-ssd} shows how the total merge time breaks
down to read, write, seek and overhead time for our algorithms. Naive
blocks and naive slices are shown as references. The huge difference
between naive blocks and naive slices is coming from both the seek
time and the write time, which suggests that seeking degrades the
write rate importantly in addition to introducing extra delays.
Cluster reads reduce the seek time and thus the read time very
substantially. Multiple reads almost anihilate the seek time and bring
the read time to a value comparable to naive slices.  The same
behavior is observed on HDD and on SSD, although the effect of seeking
is slightly lower on SSD, as expected. Read times are consistently and substantially lower than write times\todo{explain why}. The overhead time is small for
both Cluster reads and Multiple reads, although it is not negligible
for Multiple reads on HDD.
\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-creads/creads-breakdown-ssd.pdf}
    \caption{Cluster reads}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
    \caption{Multiple reads}
  \end{subfigure}
  \caption{Breakdown of total merge times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-hdd-split.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-buff-slices/buff-slices-breakdown-ssd-split.pdf}
    \caption{Buffered slices}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrite/cwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-cwrites/cwrites-breakdown-ssd.pdf}
    \caption{Cluster writes}
  \end{subfigure}
  \begin{subfigure}[b]{\columnwidth}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
    \caption{Multiple writes}
  \end{subfigure}
  \caption{Breakdown of total split times. Left column: HDD. Right column: SSD.}
  \label{fig:breakdowns-ssd-split}
  % Gnuplot file: scripts/experiment/compare_breakdown_errbar.gnuplot
\end{figure}
